Many Analystis Project

### 2021-04-29 analysis.Rmd
updated

@@

>>>>

No country level differences trending at the high end of the anxiety scale for slope/intercept covariance, but not at the low end of anxiety this pattern is reversed, leading to a canceling out ... such that overall the correlation isn't reliable [cor(Intercept,ch_s)  0.24  [-0.38, 0.77]. But worth investigating...and perhaps a more complex mixture model.

```{r}
plot(ggeffects::ggpredict(
  m1o,
  terms = c("country[all]", "ch_s[minmax]"),
  type = "re",
  ci.lvl = 0.89
)) + scale_color_viridis_d() + 
  theme_classic()
```

@@

No country level predictions in the slope/intercept covariance:

```{r}
plot(ggeffects::ggpredict(
  m2o,
  terms = c("country[all]", "bg_s[minmax]"),
  type = "re",
  ci.lvl = 0.89
)) +
  scale_color_viridis_d() +
  theme_classic()
```
